Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-08-21 paper/ifo-conclusions.tex
editing conclusion and future work

In Section~\ref{sec:optical_microphone} we demonstrate recovery of more complex signals of music and speech. 
Substituting the webcam for the increased frequency response of a photodiode read by a Raspberry Pi, we transform the interferometer into an optical microphone.
\jam{[Confirming Hannah's comment, the Pi was only necessary to read the photodiode, the webcam video I just saved onto PC and analysed directly]}
We demonstrate that the optical microphone is capable of playing back simple recordings well but that it produces unintelligible recordings of speech. 
Mains hum at $50\,{\rm Hz}$ and its harmonics dominates the photodiode output. 
This offers students the opportunity to explore speech enhancement techniques to remove it, including the well performing logMMSE estimator. 
Further avenues of exploration include a more complete model of the optical microphone transfer function, which may lead to improvements in intelligibility.

>>>>

In Section~\ref{sec:optical_microphone} we demonstrate recovery of more complex signals of music and speech. 
Substituting the webcam for the increased frequency response of a photodiode read by a Raspberry Pi, we transform the interferometer into an optical microphone.
We demonstrate that the optical microphone is capable of playing back simple recordings well but that it produces unintelligible recordings of speech. 
Mains hum at $50\,{\rm Hz}$ and its harmonics dominates the photodiode output. 
This offers students the opportunity to explore speech enhancement techniques to remove it, including the well performing logMMSE estimator. 
Further avenues of exploration include a more complete model of the optical microphone transfer function, which may lead to improvements in intelligibility.

### 2020-08-21 paper/ifo-futureWork.tex
tasks 1, 3, and 5
some general text editing and addressing comments
editing conclusion and future work

% wild speculation
%We are currently working towards two improvements of the optical microphone.

@@

A second improvement is to measure the full model of the transfer function of the system. 
With perfect knowledge of the transfer function, signal recovery is limited by the signal-to-noise ratio as an optimal matched filter could be constructed.
\jam{[check with Rob et al. about the veracity of this]}
The transfer function starts from the voltage sent to the speaker and ends with the voltage recorded by the Pi. It includes any non-linearities in the speaker itself, the speaker-mirror coupling, the separation-intensity relation Appendix~\ref{app:intensity_derivation}, and the photodiode reading. 
A schematic of the full optical microphone transfer function is shown in Figure~\ref{fig:pipeline_highlighted}.

@@

\begin{figure*}
	\includegraphics[height=.99\textwidth, angle=-90]{figures/pipeline.pdf}
	\caption{
Flowchart for the optical microphone transfer function. 
The stage inside the red, dashed box is analysed in Appendix~\ref{app:intensity_derivation}. Understanding the other stages is one part of future work. 
}
	\label{fig:pipeline_highlighted}
\end{figure*}

>>>>

\begin{figure*}
	\includegraphics[height=.99\textwidth, angle=-90]{figures/pipeline.pdf}
	\caption{
Flowchart for the optical microphone transfer function. 
The stage inside the red-dash box is analysed in Appendix~\ref{app:intensity_derivation}. Understanding the other stages is one aim of future work. 
}
	\label{fig:pipeline_highlighted}
\end{figure*}

@@

A second improvement is to measure the full model of the transfer function of the system, providing more information about how the audio signal couples with the interferometer.
% commented out whilst James is checking this
%With perfect knowledge of the transfer function, signal recovery is limited by the signal-to-noise ratio as an optimal matched filter could be constructed.
%\jam{[check with Rob et al. about the veracity of this]}
The transfer function starts from the voltage sent to the speaker and ends with the voltage recorded by the Pi. It includes any non-linearities in the speaker itself, the speaker-mirror coupling, the path length to intensity relation (Appendix~\ref{app:intensity_derivation}), and the photodiode reading. 
A schematic of the full optical microphone transfer function is shown in Figure~\ref{fig:pipeline_highlighted}.

@@
